Buildtime Trend

### 2016-01-28 buildtimetrend/btt_fosdem2016.tex
add slide with projects
some small improvements

\date[FOSDEM 2016]{FOSDEM 2016 - Brussels\\

@@

    Buildtime Trend is an Open Source application that uses (timing) data to visualise trends in a build process.

@@

    I was working on a project that was built on Travis CI:

@@

@@

>>>>

\date[FOSDEM 2016]{FOSDEM 2016\\

@@

@@

    Project with unreliable builds on Travis CI:

@@

    Buildtime Trend is an Open Source application that uses (timing) data to visualise trends in a build process

@@

    \frametitle{Who is using it}
    \pause
      \item Angular
      \item RocksDB (Facebook)
      \item phpMyAdmin
      \item Weblate
      \item MuseScore
      \item Servo
